Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 4.dev

### 2025-11-12 main.tex
Added note about four missing ages.

\subsection{Protocol}
%
We recruited 26 able-bodied young adults between 20 and 36 years old (mean 26
years) to participate in the experiments. The participants were all confident
in their cycling skills and had cycled at least once in the last month. All
participants consented to the experiment and could decline to continue at any
time. The study was approved by Delft University of Technology's Human Research
Ethics Council (record \#3897). The participants were divided into two groups.
The first group of fifteen participants performed the protocol at a belt speed
of 10~\si{\kph}(2.8~\si{\mps}) with the gain factor set to \(\kappa=3.9\) and
two weeks later the second group of eleven participants performed the protocol
at a belt speed of 6~\si{\kph} (1.7~\si{\mps}) with the gain factor set to
\(\kappa=5.2\).

>>>>

\subsection{Protocol}
%
We recruited 26 able-bodied young adults between 20 and 36 years old (mean 26
years~\footnote{Four participants' ages were lost but did fall within the
stated range.}) to participate in the experiments. The participants were all
confident in their cycling skills and had cycled at least once in the last
month. All participants consented to the experiment and could decline to
continue at any time. The study was approved by Delft University of
Technology's Human Research Ethics Council (record \#3897). The participants
were divided into two groups.  The first group of fifteen participants
performed the protocol at a belt speed of 10~\si{\kph}(2.8~\si{\mps}) with the
gain factor set to \(\kappa=3.9\) and two weeks later the second group of
eleven participants performed the protocol at a belt speed of 6~\si{\kph}
(1.7~\si{\mps}) with the gain factor set to \(\kappa=5.2\).
